---
title: "Making Choices about the EVS data"
author: "Edoardo Costantini"
date: "9/22/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(foreign) # to import .dta data
library(labelled) # to extract valriables labels
library(mice)
library(dplyr)
source("../../code/functions_genDt.R")

# Read Data ---------------------------------------------------------------

file_loc <- "/Users/Work/Data/EVS2017/data/"
  file_int <- "ZA7500_v3-0-0" # integrated data
  file_mat <- "ZA7502_v1-0-0" # matrix desing version
  miss_tag <- "_missing.txt"
  
  # Read Integrated data
  int.dt <- haven::read_dta(paste0(file_loc, file_int, ".dta"))
  dim(int.dt)

  int.df <- as.data.frame(int.dt)
  int.df$country_org <- int.df$country
  int.df$country <- factor(int.df[, "country"],
                           levels = val_labels(int.df[, "country"]),
                           labels = names(val_labels(int.df[, "country"])))
  
  # Read Matrix Design Data
  mad.dt <- haven::read_dta(paste0(file_loc, file_mat, ".dta"))
  dim(mad.dt)
  mad.df <- as.data.frame(mad.dt)
  mad.df$country <- factor(mad.df[, "country"],
                           levels = val_labels(mad.df[, "country"]),
                           labels = names(val_labels(mad.df[, "country"])))
```

# Countries and Observations: Matrix Desing VS Integrated data
Remeber from the pdf file ZA7500_mr.pdf
* The Integrated Dataset (ZA7500) contains data from 55,256 respondents and 33 countries.
* The Matrix Design Dataset (ZA7502) includes data from 10,598 respondents and the four countries (DE IS CH NL) that used the matrix design.

Observations are devided in

```{r}
lapply(list(int.dt = int.dt$mm_select_sample,
            mad.dt = mad.dt$mm_select_sample), table)
```

And you can see here what those values mean:

```{r}
val_labels(int.dt$mm_select_sample)
```

If you consider the 6 EU founding countries (Belgium, France, Germany, Italy, Luxembourg, Netherlands), this is how observations are distributed among the two datasets:

```{r}
countries  <- c("Belgium", "France", "Germany", "Italy", "Luxembourg", "Netherlands")

tab.1 <- table(int.df$country, int.df$mm_select_sample)
print(tab.1[rownames(tab.1) %in% countries, ])
tab.2 <- table(mad.df$country, mad.df$mm_select_sample)
print(tab.2[rownames(tab.2) %in% countries, ])
```
* Belgium and Luxembourg are not surveyed by EVS 2017.
* Netherlands has almost 2000 observations in group 4 (self-administered matrix)

In **conclusion**:

* Countries to keep: France, Germany, Italy, Netherlands
* Subsamples to keep: 1 and 4 from the integrated dataset

```{r}
# What to keep
subsample <- c(1, 4)
countries <- c("France", "Germany", "Italy", "Netherlands")

# Select data
int.df <- int.df %>%
  filter(mm_select_sample %in% subsample) %>%
  filter(country %in% countries)

# Check out dimensionality
dim(int.df)
```

# Variables to keep

## Generic variables by type:

```{r}
id  <- "id_cocas"
ord <- paste0("v", c(1:8, 32:39, 46:50, 53:54, 63:70, 72:84,
                     97:107, 115:168, 170:172, 176:203, 205:224, 
                     240, 242, 267:274, 280, 
                     c("174_LR", "175_LR", "239_r", "239a", "239b")))
dic <- paste0("v", c(9:31,40:45,51,57:61,71,85:95,
                     112,169,225,227,230,232,236,
                     248,259,260))
nom <- paste0("v", c(52, 62, 56, # religiosity
                     108:111, 113:114, 234, 244, 238,
                     264, 265, 266, "276_r")) 

# I will make sure the following variables are excluded
excl <- c("v27", # not really a variable in the 
          # countries we are investigating (98% of responses 
          # was same category)
          "v239a", "v239b",
          # Gated
          "v53", "v247", "v248", "v252_ISCED_1", "v170",
          # Religiosity related
          "v51", "v52", "v54",
          # respondend related questions to be discarded after use
          "v228b_r",
          # father related question to discard after use
          "v230", "v231b", "v231b_r",
          # mother related question to discard after use
          "v232", "v233b", "v233b_r"
)
```

## Political tendencies

Use a vairable measuring self reported tendency to vote for parties (recoded by
EVS into a continuous variable)

```{r}
pol <- c("v175_LR", "v174_LR")

# Frequency table
data.frame(labels = c("other missing", 
                      "not applicable", 
                      "no anwser", 
                      "dont know",
                      "left", as.character(2:9), "rigth"),
           values = sort(unique(int.df[, pol[1]])),
           freq   = as.numeric(table( int.df[, pol[1]] )),
           row.names = 1)

# If there were cases with value 44 you could do this:
int.df[which(int.df[, pol[1]] == 44), pol[1]] <- NA

# but there are not 44 cases
sapply(1:2, function(x) which(int.df[, pol[x]] == 44))

# Density Plot
plot(density(int.df[int.df[, pol[1]] > 0, 
                    pol[1]], 
             adjust = 3),
     main = "",
     xlim = c(0,10), 
     xlab  = "Left / Right vote tendency (0-10, left-right)")
```

## Age

For age, I use a constructed age vairables in "number of years old" format.

```{r}
age <- "age"
val_labels(int.df[, age])

# Density Plot
plot(density(int.df[int.df[, age]>0, age], 
             adjust = 3),
     main = "",
     xlim = c(0,100), 
     xlab  = "Age")
```

## Education

For education, I use the ISCED version and I will be treating it as 
continuous. I do this for the education of the respondent and 
their father and mother.

Values 66 need to be recoded as missings as it does not belong in any order
of education.

```{r}
# Education
edu <- c("v243_ISCED_1", # continuous is fine
         "v262_ISCED_1", 
         "v263_ISCED_1")
obsVals <- val_labels(int.df[, edu[1]]) %in% sort(unique(int.df[, edu[1]]))

data.frame(labels = names(val_labels(int.df[, edu[1]]))[obsVals],
           values = val_labels(int.df[, edu[1]])[obsVals],
           respondent = as.vector(table(int.df[, edu[1]])),
           father = as.vector(table(int.df[, edu[2]])),
           mother = as.vector(table(int.df[, edu[3]])),
           row.names = 1)

# If there were cases with 66 observed, you woudl need to fix it:
# but there are none
sapply(edu, function(x) which(int.df[, x] == 66))

for (j in edu) {
  int.df[which(int.df[, j] == 66), j] <- NA
}
```

## Job / Profession / SES / income

The EGP classification is used to record the Socio-economic status of respondents. 
Reference paper for this classifcation is Ganzeboom Treiman 1996. After the single
imputation is done I will collapse the 10 categories into 3: (I) lower/working class;
(II) middle class; (3) higher class. For this partitioning you could look back at
D'Hooge et al 2018.

```{r}
# Job / SES
SES <- "v246_egp"
obsVals <- val_labels(int.df[, SES]) %in% sort(unique(int.df[, SES]))

data.frame(labels = names(val_labels(int.df[, SES]))[obsVals],
           values = val_labels(int.df[, SES])[obsVals],
           freq = as.vector(table(int.df[, SES])),
           row.names = 1)

# Income
inc <- "v261_ppp"
```

## Denomination and Religiosity

These variables need a bit of recoding:
* Denomination is recorded with two variables: 1 dichotomous asking whether 
  someone belongs to one; (2) one follow up question asking to which 
  denomination they belong to (I want them in 1 variable).
* Religiosity is recorded with higher frequency being smaller numbers
  (I want the opposite)

```{r}
den <- c("v51", # do you belong
         "v52") # which denomination do you belong to?
rel <- c("v54", "v55") # apart from ... how often services? for religiosity

# Denomination Merge
                        # If you belong to a denomination, to which?
  den_comb <- case_when(int.df[, den[1]] == 1 ~ int.df[, den[2]],
                        # You don't belong
                        int.df[, den[1]] == 2 ~ 0)
  
  val_labels(den_comb) <- c(val_labels(den_comb)[val_labels(den_comb) < 0],
                            "No Religion" = 0, 
                            val_labels(den_comb)[val_labels(den_comb) > 0])
  int.df$den_comb <- den_comb # save it
  
  # Frequency Table
  obsVals <- val_labels(den_comb) %in% sort(unique(den_comb))
  data.frame(labels = names(val_labels(den_comb))[obsVals],
             values = val_labels(den_comb)[obsVals],
             freq = as.vector(table(den_comb)),
             row.names = 1)

# Religiosity Recode
  # I do not want to change this codeing at this level. I will change things
  # only at the analysis model level.
  # rel_invCod <- sapply(1:length(rel), function(x) match(int.df[, rel[x]], 7:1))
  # 
  # # Frequency comparison
  # # Present
  # data.frame(old.v54 = table(int.df[int.df[, rel[1]]>0, rel[1]],
  #                        dnn = c("rel")),
  #            new.v54 = table(rel_invCod[,1], dnn = c("rel"))[7:1])
  # # Past
  # data.frame(old.v55 = table(int.df[int.df[, rel[2]]>0, rel[2]],
  #                        dnn = c("rel")),
  #            new.v55 = table(rel_invCod[,2], dnn = c("rel"))[7:1])
  # 
  # # Keep new recoded version
  # int.df[, rel] <- rel_invCod
```

## Marital Status

Nothing special to report but it's an important variable for the substantive 
model, so it deserves a bit of attention just to make sure I know it.

```{r}
mart <- "v234"
obsVals <- val_labels(int.df[, mart]) %in% sort(unique(int.df[, mart]))

data.frame(labels = names(val_labels(int.df[, mart]))[obsVals],
           values = val_labels(int.df[, mart])[obsVals],
           freq = as.vector(table(int.df[, mart])),
           row.names = 1)
```

## Sex and Union Membership

Nothing special to report but it's an important variable for the substantive 
model, so it deserves a bit of attention

```{r}
# Sex
sex <- "v225"
obsVals <- val_labels(int.df[, sex]) %in% sort(unique(int.df[, sex]))

data.frame(labels = names(val_labels(int.df[, sex]))[obsVals],
           values = val_labels(int.df[, sex])[obsVals],
           freq = as.vector(table(int.df[, sex])),
           row.names = 1)

# Union Membership
um <- "v11"
obsVals <- val_labels(int.df[, um]) %in% sort(unique(int.df[, um]))

data.frame(labels = names(val_labels(int.df[, um]))[obsVals],
           values = val_labels(int.df[, um])[obsVals],
           freq = as.vector(table(int.df[, um])),
           row.names = 1)
```

## Country Variables

Here we manage the country variables. First, I need to create a map
of country labels and ISO codes.

```{r}
ISO3116 <- data.frame(name = names(val_labels(int.df[, "v231b_r"])), 
                      code = as.numeric(val_labels(int.df[, "v231b_r"])))
head(ISO3116, 20)
```

Then I need to create a variable that records the country of birth of the
respondent, combining the variable related to the country of interview 
and the question of whether the respondant was born in the same country.

```{r}
# Interviee country of birth
re_intw  <- ISO3116$name[match(int.df[, "country_org"], ISO3116$code)] # interview
re_alter <- ISO3116$name[match(int.df[, "v228b_r"], ISO3116$code)] # birth
re_cb <- case_when(re_alter == "not applicable" ~ re_intw, # country of birth
                   re_alter != "not applicable" ~ re_alter)
# Check
set.seed(2042)
random_obs <- sample(1:length(re_cb), 10)
data.frame(interview = re_intw, 
           alternative = re_alter, 
           respondent = re_cb)[random_obs, ]
```

The next step is to combine similarly the variables realted to the 
country where mother and father were born.

```{r}
# Father's country
  fa_alter <- ISO3116$name[match(int.df[, "v231b_r"], ISO3116$code)]
  fa_cb    <- case_when(int.df[, "v230"] == 1 ~ re_intw,
                        int.df[, "v230"] == 2 ~ fa_alter)

  # Check
  data.frame(re_intw, fa_alter, fa_cb)[random_obs, ]

  # Add to dataset
  int.df$fa_cb <- fa_cb
  father_index <- c("fa_cb")

# Mother's country
  ma_alter <- ISO3116$name[match(int.df[, "v233b_r"], ISO3116$code)]
  ma_cb <- case_when(int.df[, "v232"] == 1 ~ re_intw,
                     int.df[, "v232"] == 2 ~ ma_alter)
  
  # Check
  data.frame(re_intw, ma_alter, ma_cb)[random_obs, ]
  
  # Add to dataset
  int.df$ma_cb <- ma_cb
  mother_index <- c("ma_cb")
  
# Similarity between the two variables
  data.frame(re_intw, fa_alter, ma_alter)[which(fa_alter != ma_alter)[1:10], ]
  mean(fa_alter != ma_alter) * 100
```
Because the two are very similar, I will keep only one of the two variables 
(mother).

# Perform Selection and compare with previous data

```{r}
  # Prepare vector of column names to keep
  var_indx <- unique(c(id, "country", ord, dic, nom, pol, age, edu, SES, inc, 
                       "den_comb", rel, 
                       mart, sex, um, 
                       "ma_cb"))
  var_vec <- var_indx[!var_indx %in% excl]

  # Perform Variable Selection
  EVS2017 <- int.df %>%
    select(all_of( var_vec ))
  dim(EVS2017)
  dim(int.df)
```

Let's create vectors containing the names of all possible columns (allCol),
of all columns actively kept up to this point (keptCol), and of columns that
have been left out (lostCol). The latter vector is used as a list of variables
to be screened: are the variables there really desinated to be left out? As I
proceed in this document I will exclude vairables from lostCol that have been
screened: they will either be included in the list of variables to keep or 
forgotten completly.

```{r}
  allCol  <- colnames(int.df)
  keptCol <- colnames(EVS2017)
  lostCol <- allCol[which(!allCol %in% keptCol)]
  lostCol
```

## Step 0: get rid of variables wrongly kept

Many of the vairables asking an opition on different related topics include
final summary variables that are not important for the purposes of this 
study. For example, consider:

```{r}
# v20 = 1
int.df[int.df$v20 == 1, c("v20", paste0("v", 9:19))][1:5, ]

# v20 = 2
int.df[int.df$v20 == 2, c("v20", paste0("v", 9:19))][1:5, ]
```

which shows that v20 registers value 1, for all observations that have value 2
(not mentioned on vairblaes v9 to v19). Hence, we look for all variable names
including "none (spontaneus)" and get rid of those as they are all replicated
info as v20.

First, identify the precise variable label to look for

```{r}
var_label(int.df$v20)
```

"(spontaneous)" is the winner. Now, grep it among all variable names and make
sure you are not keeping these variables.

```{r}
data.frame(Var_Name = grep("(spontaneous)", 
                           sapply(int.df, var_label),
                           value = TRUE))
```

## Step 1: get rid of meta data and differently scaled variables

Let's try to study them. First keep only names of **columns that include "v"**,
the others are all meta data variables (except for age that is already included
in one form)

```{r}
  lostCol <- lostCol[grep("^[v][0-9]", lostCol)]
  # lC.v is short for lostCol.variables
```

Then, we can get rid of variables we **already have included in some form** (e.g.
education, SES):

```{r}
toMatch <- c("edu", "ISCED", "egp", # education
             "ESeC", "ISCO", "ISEI", "SIOPS", # job
             "GB", "DK", # country specific for not relevant countries
             "weight"
)

var.duplicate <- grep(paste(toMatch, collapse = "|"), 
                  lostCol, value = TRUE)
var.duplicate
lostCol <- lostCol[!lostCol %in% var.duplicate] #
```

The we can see which **variables "without notes"** we have left out.
Keeping in mind that I have conciously got rid of some of these vairables with
the "excl" vector, I want to ingore those.

```{r}
  var.number <- grep("v[0-9]*$", lostCol, value = TRUE)
  data.frame(Var_Desc = sapply(int.df[, var.number[!var.number %in% excl]], var_label))
```

Some of these variables are asked only to subseted of the sample. For example,
consider v241 or v236, asked to people that have more 1 person in houseold or
that have a registered partnership, respectively. I leave these variables in
the ditch-bucket because creating harmonized variables would be too much 
work without any particular benefit for the purpose of this paper. Similar
fate is assured for spouse related questions (e.g. v253)

### Q28: v96 and its alternatives

You can see in the following output that those variables are just recoded 
information contained in the itesm between v85 and v95. For the purpose
of my study, I do not need them.

```{r}
t(sapply(int.df[, c(paste0("v", 85:95))], table))
t(sapply(int.df[, c("v96", "v96a", "v96b")], table))
# v96, 1 = people that responded 2 (not mentioned) to all other questions
int.df[int.df$v96 == 1, c(paste0("v", 85:95), "v96a")]
# v96a, 1 = giving -1 (DK) to all items of question 28
int.df[int.df$v96a == 1, c(paste0("v", 85:95), "v96a")]
# v96b, 1 = giving -1 (no answer) to all items of question 28
int.df[int.df$v96b == 1, c(paste0("v", 85:95), "v96a")]
```

###Q57: v204 - protecting environment vs. economic growth

Let's see how people have responded to this question.

```{r}
round(prop.table(table(int.df$v204)), 3)*100
```

6% have given an "other" answer. Altought this is not a large portion
of the respondents it still requires and ad-hoc solution I will not
be taking. Hence this question remains in the ditch-bucket.

### Q74: Live w/ a partener?
```{r}
round(prop.table(table(int.df$v236)), 3)*100
```
Question asked only to people haveing registered partnership. Remains in
ditch-bucket because of high rate of not applicable answers.

### Q98: Household form

To make the ppp version look that good I needed to use the adjust argument
but it still seems like a variable that is closer to a normal disitrbution
than v261. Hence, I keep v261_ppp for measuring income.

```{r}
table(int.df$v261)
table(int.df$v261_ppp)

par(mfrow=c(1,2))

plot(density(int.df$v261[int.df$v261 > 0], adjust = 2),
     main = "v261", xlim = c(0, 10))
plot(density(int.df$v261_ppp[int.df$v261_ppp > 0], adjust = 6),
     main = "v261_pp", xlim = c(0, 10))
```

### Size of town
v276 was initially part of these left out variables. However, it might be interesting.
Considering it's distribution, I will consider it as a categorical variable.
```{r}
# Freq table
table(int.df$v276)

# Distribution
hist(int.df$v276[int.df$v276 > 0], main = "Respondent Town Size (v276)")
```

In **conclusion** we can get rid of these variables for good

```{r}
# Forget about vairables of form v###
lostCol <- lostCol[!lostCol %in% var.number]
```

## Step 2

Now let's look at the recoded versions of other variables (checking I'm keeping
the one I want)

```{r}
# Look at var._r questions
var._r <- sapply(int.df[, grep("_r", lostCol, value = TRUE)], var_label)
data.frame(Var_Label = var._r)
```

### Income (v262_r)

v262_r stands out as a possibility, but then I realize it is just a 
variable w/ 3 categories: lower, midium, higher. Hence, no better
than v261_ppp at measuring income.

In **conclusion**, we can get rid of all of them

```{r}
# Forget about var._r columns
lostCol <- lostCol[!lostCol %in% names(var._r)]
```

## Step 3: looking at variables with letter right after number

```{r}
# Look at var.letter questions
var.letter <- sapply(int.df[, 
                            grep("v[0-9]*[a-z]$", lostCol, value = TRUE)], 
                     var_label)
data.frame(Var_Label = var.letter)
```

These vairables belong to one of these groups:

* "dont know/no answer" to previous question - these are not in need 
  to be kept as their value is already reported as a missing value in
  the previous questions (are they? check with one) <---- CHECK!!!

* country of birth -  this info is already recorded in other variables
  I have actively kept.
  
* gated question - questions related to partners that are asked only
  to people that do have partners.
  
* time of interview - meta data that slipped through

In **conclusion**, we can get rid of all of them

```{r}
# Forget about var._r columns
lostCol <- lostCol[!lostCol %in% names(var.letter)]
```

## Step 4: looking at country specific variables
### cs like variables
Let's start with vairables with the "_cs" tag in their name

```{r}
var._cs <- sapply(int.df[, 
                         grep("_cs$", lostCol, value = TRUE)
                         ], 
                  var_label)
data.frame(Var_Label = var._cs)
```

You notice that all of the "_cs" vairable are education or denomination related.
You have already kept everything that is interesting regardin this infomration
in a more suitable format in the "Variables to keep" section. Hence, you will 
discard this part of the data for sure.

```{r}
# Forget about var._cs$ columns
lostCol <- lostCol[!lostCol %in% names(var._cs)]
```

Next you can focus on more complex cs variables: the "_cs_DE" group.

```{r}
var._cs_ <- sapply(int.df[, 
                         grep("_cs", lostCol, value = TRUE)
                         ], 
                  var_label)
data.frame(Var_Label = var._cs_)
```

These variables are all education related and require a bit more investigation
to make sure that we are recording the info in the other educational variables.
As always, there are four educational vairables: respondent, father, mother,
possible partner. Looking at the codebook it seems clear that the variables
"v2**_cs_DE1" are measuring education based on the specifc german system, while
"v2**_ISCED_1" are measuring the same info but standardized. You can check this:

```{r}
# Select just Germany observations
int.de <- int.df %>%
  filter(country == "Germany")

# Same number of observations (i.e. not a matrix specific question)
sapply(int.de[, c("v243_ISCED_1", "v243_cs_DE1", "v243_cs_DE2")], 
       function(x) sum(table(x)))
```

As a result, I decide to exclude them as well.

```{r}
# Forget about var._cs$ columns
lostCol <- lostCol[!lostCol %in% names(var._cs_)]
```

### Other Germany Specific questions

```{r}
var._DE <- sapply(int.df[, 
                        grep("[0-9]_DE", lostCol, value = TRUE)
                        ], 
                 var_label)
data.frame(Var_Label = var._DE)
```

Once again, I need to check consistency of information between what is recorded
in the non-DE specific variables for the German respondents. Let's see:

```{r}
# Excluding the people that responded to the matrix desing, no one respondend
table(int.df[int.df$country == "Germany", "v72_DE"])

# In the matrix desing people did answer to this question
table(mad.df[mad.df$country == "Germany", "v72_DE"])
```

The "_DE" quesitons were asked to the matrix design respondents. We are not
considering those respondents, so I can forget about these questions.

```{r}
# Forget about var._cs$ columns
lostCol <- lostCol[!lostCol %in% names(var._DE)]
```

### N* regional codes

```{r}
var._N <- sapply(int.df[, 
                        grep("_N[0-9]", lostCol, value = TRUE)
                        ], 
                 var_label)
data.frame(Var_Label = var._N)
```

This level of detail of where interview took place is not particularly 
interesting for the purpuses of this study. As variables covering this info
I already have the country where the interview took place (for "cultural"
reasoning) and the size of the town the respondent lives in (for urbanistic
control).
As a result, I decide to forget about them forever.

```{r}
# Forget about var._N$ columns
lostCol <- lostCol[!lostCol %in% names(var._N)]
```

### Italian Experimental Questions

```{r}
# Which vairables are we talking about
var._IT <- sapply(int.df[, 
                        grep("_IT", lostCol, value = TRUE)
                        ], 
                 var_label)
data.frame(Var_Label = var._IT)

# Proportion of respondends per category
round(prop.table(table(int.df$v24a_IT)), 3)
```

Experimental questions are left out because we have too few respondents on them

```{r}
# Forget about var._IT$ columns
lostCol <- lostCol[!lostCol %in% names(var._IT)]
```

### Neterlands and other country specific questions "_11c"

```{r}
# Which vairables are we talking about
var._11c <- sapply(int.df[, 
                        grep("_11c", lostCol, value = TRUE)
                        ], 
                 var_label)
data.frame(Var_Label = var._11c)
```

Again, we need to check how many respondents were given these questions.
For this specific question, 4 countries were considered: Denmark, Finalnd, 
Iceland, and the Netherlands. We only have this latter country in our 
dataset. Let's focus on it.

```{r}
# Select just Netherlands observations
int.nl <- int.df %>%
  filter(country == "Netherlands")
```

Notice how, 1718 observations were not given the standard version for these
questions.

```{r}
sapply(int.df[int.df$country == "Netherlands", paste0("v", 133:141)], 
       function(x) table(x))
```

Which are the 1718 onservations to which questions "_11c" are given.

```{r}
sapply(int.nl[, names(var._11c)], 
       function(x) {
        temp <- data.frame(table(x[x > -4]))[,2]
        names(temp) <- data.frame(table(x[x > -4]))[,1]
        c( temp, tot = sum(temp) )
       }
       )
```

Now, for the purpuses of this study, it is completly fine to mix the answers of
the two quesitons: I want respondents in the Netherlands to have just one variable
for this set.

```{r}
int.nl.fix <- int.df

var_nams <- paste0("v", 133:141)
cnt_indx <- int.nl.fix$country == "Netherlands" # rows from NL

for (v in var_nams) {
  var_indx <- int.nl.fix[, v] == -4 # rows did not recieve Q
  
  toFill <- int.df[cnt_indx & var_indx, paste0(v, "_11c")]
  
  int.nl.fix[cnt_indx & var_indx, v] <- toFill
}
```

And we can check that it worked for one sample variable:

```{r}
v <- var_nams[1] # choose sample variable
var_indx <- int.df[, v] == -4 # rows did not recieve Q

# Asked version 2, keeps version 2 as response
cbind(
  int.df[cnt_indx & var_indx, c(v, paste0(v, "_11c"))],
  int.nl.fix[cnt_indx & var_indx, v]
)[1:5, ]

# Asked version 1, keeps version 1 as response
cbind(
  int.df[cnt_indx & !var_indx, c(v, paste0(v, "_11c"))],
  int.nl.fix[cnt_indx & !var_indx, v]
)[1:5, ]
```

After this is done, I can get rid of this country specific questions:

```{r}
# Forget about var._11c columns
lostCol <- lostCol[!lostCol %in% names(var._11c)]
```

### Post-materialism costructed variable (v111_4)

v111_4 is a combination of variable v110 and v111 that measures 
postmaterialism. I do not particularly care about this construct
in my substantive models, so I will keep the original vairables
as separated.

```{r}
# Forget about v111_4 column
lostCol <- lostCol[!lostCol %in% "v111_4"]
```

And now the object lostCol is empty: I have checked all the variables that
I had originally excluded to confirm their exclusion.

# Coding of variables

## Direction
Most ordered variables have a coding scheme that is not intuitive: higher score
means lower itensity. For example, consider

EVS2017

```{r}
val_labels(EVS2017$v6)[-(1:8)]
```

On the other end, others are perfectly fine:

```{r}
var_label(EVS2017$v156)
val_labels(EVS2017$v156)[-(1:8)]
```

For prediction and imputation this difference is not important as long as 
things are consistent. Therefore, I leave the coding as it is done in the data 
preparation for imputation, but I will take care of it for analysis models.

## Dummies

Just make sure that important variables are coded in a way that makes sense to you.