\maketitle
\section{Simulation Studies}

The simulation study was broken up in two separate experiments: (1) the first was used to define a baseline comparison 
of the methods on multivariate normal data in both high and low dimensional conditions; (2) the second was used to 
assess the performance of the methods in the presence of a latent structure, in order to reflect the fundamental
structure of social survey data.

\subsection{Methods: two simulation studies}

\paragraph{Data generations}
	Describe normal multivariate distribution used for the first simulation study 

	Describe latent variable data generation for the second simulation study.

\paragraph{Missing data imposition}
	Describes how missing data are imposed on the generated data (target variables, response models)

\paragraph{Analysis model(s)}
	Describe the saturated model (MLE estimates of means and variances), linear models, 
	Confirmatory Factor Analysis.

\paragraph{Criteria}
	Description and formulas for bias and confidence interval coverage.

	Description of multivariate measure of distance for groups of parameters

\paragraph{Procedure}
	Summary description of crossed conditions.

	Description of 1 data replication steps (data gen, imputation, analysis, pooling, averaging results)

\subsection{Results}

\paragraph{Bias}
	Report results of comparison in terms of estimates bias for relevant parameters

	Given concise idea of implications. Avoid higher level comparisons.
	
\paragraph{Confidence Interval Coverage}
	Report results of comparison in terms of confidence interval coverage of the "true" values of parameters 

	Given concise idea of implications. Avoid higher level comparisons.
	

